Hypertension and microbiome

### 2019-01-03 rrbiome.Rmd
More permutations for adonis

 ```{r adonis calculation, cache = FALSE}
if (!file.exists("rds/adonis.species.rds")) {
    adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                    covariates = "BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09",
                    npermutations = 99)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
} else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```

>>>>

 ```{r adonis calculation, cache = FALSE}
if (!file.exists("rds/adonis.species.rds")) {
    adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                    covariates = "BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09",
                    npermutations = 500)
     saveRDS(adonis.species, file = "rds/adonis.species.rds")
} else {
     adonis.species  <- readRDS("rds/adonis.species.rds")
}
```
